\Large Clustering Trips Identified from Automatic Number \\ Plate Recognition Camera Scans

### 2018-02-01 paper.tex
A few fixes and title change

\title{\Large Clustering Vehicle Trips Identified from Automatic \\ Number Plate Recognition Camera Scans}
\author{Pedro M. Pinto Silva \thanks{School of Computing, Newcastle University, United Kingdom}
\and
Matthew Forshaw\footnotemark[1]
\and
Stephen McGough\footnotemark[1]}
\date{}

@@

\begin{abstract} \small\baselineskip=9pt This is the text of my abstract. It is a brief
description of my
paper, outlining the purposes and goals I am trying to address.\end{abstract}

>>>>

\title{\Large Clustering Trips Identified from Automatic Number \\ Plate Recognition Camera Scans}
\author{Pedro M. Pinto Silva \thanks{School of Computing, Newcastle University, United Kingdom}
\and
Matthew Forshaw\footnotemark[1]
\and
Stephen McGough\footnotemark[1]}
\date{}

@@

\begin{abstract} \small\baselineskip=9pt Increases in price and performance of automatic number plate recognition over the last two decades has led to  by law enforcement and urban traffic control. In this work we show how \end{abstract}
